Title of submission to PLOS journal

### 2019-08-26 docs/manuscript_draft.tex
updated manuscript

\hypertarget{materials-and-methods}{%
\section{Materials and Methods}\label{materials-and-methods}}

@@

@@

\hypertarget{remove-eggs}{%
\subsubsection{Remove eggs}\label{remove-eggs}}

@@

@@

\hypertarget{remove-chicks}{%
\subsubsection{Remove chicks}\label{remove-chicks}}

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\hypertarget{figures}{%
\section{Figures}\label{figures}}

@@

\textbf{Fig 2. Female characterization dendrogram with trait heatmap.}.
Most pituitary samples form a single cluster. More hypothalamus samples
cluster with gonads than with pituitary. The top panel is a dendrogram
showing Euclidean distance of sample. Females (white), males (red),
gonad (white), hypothalamus (pink), pituitary (red).

@@

\textbf{Fig 3. Male characterization dendrogram with trait heatmap.}. As
with females, most pituitary samples form a single cluster, while more
hypothalamus samples cluster with gonads than with pituitary.

>>>>

Aim I lays the necessary groundwork for establishing a pattern of
correlative relationships between observed changes in gene expression
and patterns of parental behavior. With this pattern established, we can
proceed with experimental manipulations proposed under Aim III to
determine causation.

\hypertarget{materials-and-methods-and-results}{%
\section{Materials and Methods and
Results}\label{materials-and-methods-and-results}}

@@

\hypertarget{characterize-changes-in-neural-gene-expression-during-parental-care-transitions}{%
\subsection{Characterize changes in neural-gene expression during
parental care
transitions}\label{characterize-changes-in-neural-gene-expression-during-parental-care-transitions}}

Our working hypothesis is that distinct changes in transcription occur
in the brain at the anticipation of, during, and in response to two
different types of parental care: incubation behavior and hatchling
care.

\hypertarget{overall-patterns-of-sample-similarity}{%
\subsubsection{overall patterns of sample
similarity}\label{overall-patterns-of-sample-similarity}}

This ecludian clustering shows many clusters are heterogenous,
consisting of sames from all tissues types, both sexes, and from
multiple treatment groups.

\hypertarget{subset-by-sex-and-tissue}{%
\subsection{subset by sex and tissue}\label{subset-by-sex-and-tissue}}

The rest of the analyses are peformed on each sex and tissue group
separately, a 2 x 3 design.

\includegraphics{manuscript_draft_files/figure-latex/unnamed-chunk-4-1.pdf}

\textbf{Fig 2. The magnitude of gene expression changes between each
parental transition}. 4-5K genes are differentially expressed beteen
control birds and their nest buliding conspecifics in all tissues except
the male gonad. 500 - 1000 genes are differentially expressed in the
female pituitary from mid-late incubation as well as in the female
hypothalamus and pituitary from hatch to nestingly care day 5.

\includegraphics{../figures/characterization/musicalgenes-05.png}

@@

\hypertarget{remove-eggs-or-chicks}{%
\subsubsection{Remove eggs or chicks}\label{remove-eggs-or-chicks}}

@@

\includegraphics{../figures/sexes/offspringremoval-1.png}

@@

@@

\hypertarget{supplementary-figures}{%
\section{Supplementary Figures}\label{supplementary-figures}}

@@

\textbf{Fig S1a. Female characterization dendrogram with trait
heatmap.}. Most pituitary samples form a single cluster. More
hypothalamus samples cluster with gonads than with pituitary. The top
panel is a dendrogram showing Euclidean distance of sample. Females
(white), males (red), gonad (white), hypothalamus (pink), pituitary
(red).

@@

\textbf{Fig S1b. Male characterization dendrogram with trait heatmap.}.
As with females, most pituitary samples form a single cluster, while
more hypothalamus samples cluster with gonads than with pituitary.
